Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-03-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added citations to pres

	\item Aspiration interventions can backfire
	\begin{itemize_2pt}
		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzie2021a}
		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
		\item[] \quad \citet[See also,][]{Galiani2018}
	\end{itemize_2pt}

@@

	\item Classical study: \textcolor{camel}{Drexler, Fischer, \& Schoar (2014)}
	\begin{itemize_2pt}
		\item Comparison of heuristics-based and standard accounting training with 1,193 micro-entrepreneurs in the Dominican  Republic
		\item Null effect for full sample
		\item[] $\rightarrow$ Statistical power limited due to substantial missing sales data
		\item[] $\rightarrow$ \textcolor{bdf}{Larger gains with heuristics-based training for less educated entrepreneurs}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_2pt}
		\item \textcolor{camel}{Arr\'aiz et al. (2019)} compare 4-hours heuristics-based finance training with standard finance and accounting program among 2,408 micro-entrepreneurs in Ecuador 
		\begin{itemize_2pt}
			\item Heuristics-based training increases daily business sales and profits by about 8\% each
			\item Effects driven by \textcolor{bdf}{women} and entrepreneurs with \textcolor{bdf}{lower cognitive scores}
		\end{itemize_2pt}

@@

		\item Points of critique
		\begin{itemize_2pt}
			\item \textcolor{bdf}{Limited target group} of cognitively challenged
			\item \textcolor{bdf}{Limited scope} (mostly confined to accounting practices)
			\item So far \textcolor{bdf}{no long-term follow-up} (studies use 1-year endlines)
			\item \textcolor{camel}{Cole and Schoar (2019)} find more mixed evidence for text-based rule-of-thumb assistance among micro-entrepreneurs in India and The Philippines
		\end{itemize_2pt}

@@

	\item \textcolor{camel}{Campos et al. (2017)} compare mindset training to standard business training among 1,500 micro-entrepreneurs in Togo
	\begin{itemize_2pt}
		\item 36 hours classroom instruction
		\item 4 monthly 3-hours one-on-one follow-ups by trainer
		\item USD 750 per person
		\item[] $\rightarrow$ \textcolor{bdf}{Initiative training improves business profits by 30\% over 2.5 years}
		\item[] \quad (Standard business training improves profits by 11\%)
		\item[] $\rightarrow$ \textcolor{bdf}{Costs amortized within a year through firm profits}
	\end{itemize_2pt}

@@

Points of critique
\begin{itemize_2pt}
	\item \textcolor{bdf}{Probably limited target group}
	\item Not clear whether standard curriculum and personal initiative training are \textcolor{bdf}{complements or substitutes}
	\item \textcolor{camel}{Alibhai et al. (2019)} and \textcolor{camel}{Ubfal et al. (2019)} find \textcolor{bdf}{mixed results with lower treatment intensity}
	\item No work yet on whether \textcolor{bdf}{classroom training and/or one-on-one follow-ups} necessary and/or sufficient conditions for success
\end{itemize_2pt}
\end{frame}

@@

\begin{itemize_2pt}
	\item Successful business owners mentor smaller firms (\textcolor{camel}{Brooks et al., 2018})
	\begin{itemize_2pt}
		\item Random assignment of mentors or standard business training to 372 female micro-entrepreneurs in Kenya
		\item Mentorship dyads
		\begin{itemize_2pt}
			\item Mentors local entrepreneurs from more profitable firms
			\item \textcolor{bdf}{Encouragement of weekly meetings at mentor's firm for one month}
			\item Many dyads continue meeting for more than one year
		\end{itemize_2pt}

@@

		\item \textcolor{camel}{McKenzie and Puerto (2020)} find no impact of a 5-months mentoring scheme among female micro-entrepreneurs in Kenya
	\end{itemize_2pt}
\end{itemize_2pt}

@@

	\item Firms matched among peers \textcolor{camel}{(Cai and Szeidl, 2018)}
	\begin{itemize_2pt}
		\item Random assignment of \textcolor{bdf}{peer group meetings} among 2,820 SMEs in China
		\item Monthly meetings with 9 peers for 10 months
		\item Peer groups of different sizes and sector compositions

>>>>

	\item Aspiration interventions can backfire
	\begin{itemize_2pt}
		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzie2021a}
		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
		\item[] \quad \citep[see also,][]{Galiani2018}
	\end{itemize_2pt}

@@

	\item Classical study: \citet{Drexler2014}
	\begin{itemize_2pt}
		\item Comparison of heuristics-based and standard accounting training with 1,193 micro-entrepreneurs in the Dominican  Republic
		\item Null effect for full sample
		\item[] $\rightarrow$ Statistical power limited due to substantial missing sales data
		\item[] $\rightarrow$ \textcolor{bdf}{Larger gains with heuristics-based training for less educated entrepreneurs}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_2pt}
		\item \citet{Arraiz2019} compare 4-hours heuristics-based finance training with standard finance and accounting program among 2,408 micro-entrepreneurs in Ecuador 
		\begin{itemize_2pt}
			\item Heuristics-based training increases daily business sales and profits by about 8\% each
			\item Effects driven by \textcolor{bdf}{women} and entrepreneurs with \textcolor{bdf}{lower cognitive scores}
		\end{itemize_2pt}

@@

		\item Points of critique
		\begin{itemize_2pt}
			\item \textcolor{bdf}{Limited target group} of cognitively challenged
			\item \textcolor{bdf}{Limited scope} (mostly confined to accounting practices)
			\item So far \textcolor{bdf}{no long-term follow-up} (studies use 1-year endlines)
			\item \citet{Cole2018} find more mixed evidence for text-based rule-of-thumb assistance among micro-entrepreneurs in India and The Philippines
		\end{itemize_2pt}

@@

	\item \citet{Campos2017} compare mindset training to standard business training among 1,500 micro-entrepreneurs in Togo
	\begin{itemize_2pt}
		\item 36 hours classroom instruction
		\item 4 monthly 3-hours one-on-one follow-ups by trainer
		\item USD 750 per person
		\item[] $\rightarrow$ \textcolor{bdf}{Initiative training improves business profits by 30\% over 2.5 years}
		\item[] \quad (Standard business training improves profits by 11\%)
		\item[] $\rightarrow$ \textcolor{bdf}{Costs amortized within a year through firm profits}
	\end{itemize_2pt}

@@

Points of critique
\begin{itemize_2pt}
	\item \textcolor{bdf}{Probably limited target group}
	\item Not clear whether standard curriculum and personal initiative training are \textcolor{bdf}{complements or substitutes}
	\item \citet{Alibhai2019} and \citet{Ubfal2020} find \textcolor{bdf}{mixed results with lower treatment intensity}
	\item No work yet on whether \textcolor{bdf}{classroom training and/or one-on-one follow-ups} necessary and/or sufficient conditions for success
\end{itemize_2pt}
\end{frame}

@@

\begin{itemize_2pt}
	\item Successful business owners mentor smaller firms \citep{Brooks2018}
	\begin{itemize_2pt}
		\item Random assignment of mentors or standard business training to 372 female micro-entrepreneurs in Kenya
		\item Mentorship dyads
		\begin{itemize_2pt}
			\item Mentors local entrepreneurs from more profitable firms
			\item \textcolor{bdf}{Encouragement of weekly meetings at mentor's firm for one month}
			\item Many dyads continue meeting for more than one year
		\end{itemize_2pt}

@@

		\item \citet{McKenziePuerto2021} find no impact of a 5-months mentoring scheme among female micro-entrepreneurs in Kenya
	\end{itemize_2pt}
\end{itemize_2pt}

@@

	\item Firms matched among peers \citep{Cai2018}
	\begin{itemize_2pt}
		\item Random assignment of \textcolor{bdf}{peer group meetings} among 2,820 SMEs in China
		\item Monthly meetings with 9 peers for 10 months
		\item Peer groups of different sizes and sector compositions
